### 2018-03-16 papers.tex
papers.tex: Give up on these TODOs
Two new reviews
Two last-minute reviews
Update ToC and remove build dependency on last year's reviews

\addproceedings{These papers are so awesome few can bear to look away!}

% TODO: Add any new reviews
% TODO: Spellcheck papers list
% TODO: Add ice skating photos?
% TODO: Change title page font

\addtrack{Bear track}{Strong Accept}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Joe Doyle}
	{}
	{SIGBOVIK_2017_paper_14}
	{3cm}
	{}
\addpaper
	{I'm on vacation so I'm submitting a vacation picture instead of a paper, or, perhaps, a vacation photo in the format of a paper; I hope a predatory open access journal e-mails me about this article}
	{Jim McCann}
	{}
	{SIGBOVIK_2017_paper_15}
	{0cm}
	{}

\addtrack{Mule track}{I'm Going to Use This!}
\addpaper
	{Who sorts the sorters?}
	{Alexander R.\ Frieder}
	{}
	{SIGBOVIK_2017_paper_39}
	{0cm}
	{}
\addpaper
	{Objectionability: A computational view of mathematical computation}
	{Cameron Wong and Dez Reed}
	{}
	{SIGBOVIK_2017_paper_18}
	{1cm}
	{}
\addpaper
	{Towards a well-defined and secure flirtation protocol}
	{Rowan Copley}
	{}
	{SIGBOVIK_2017_paper_72}
	{2cm}
	{}
\addpaper
	{A solution to the two-body problem}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_29}
	{3cm}
	{}

\addtrack{Magpie track}{Who Said Money Can't Buy...}
\addpaper
	{Call For Partners: Romance with rigor}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_30}
	{3cm}
	{}
\addpaper
	{Nano electronic transplant in brain and eyes to analyze and process human thoughts and emotions}
	{Chinmaya Lele}
	{}
	{SIGBOVIK_2017_paper_66}
	{1cm}
	{}
\addpaper
	{Grant proposal: Monetary policy of sparkly things}
	{Pete, Luna, and Stefan Muller}
	{}
	{SIGBOVIK_2017_paper_62}
	{1cm}
	{}

\addtrack{Monkey track}{It's Only a Game Theory}
\addpaper
	{Is it Percival time yet?: A preliminary analysis of Avalon gameplay and strategy}
	{Yuzuko Nakamura}
	{}
	{SIGBOVIK_2017_paper_92}
	{0cm}
	{}
\addpaper
	{Dr.\ Boozehead, or How I learned to stop worrying and get drunk: Design principles and analysis of drinking games in the silicon age}
	{Kelvin M.\ Liu-Huang and Emily J.\ Simon}
	{}
	{SIGBOVIK_2017_paper_79}
	{0cm}
	{}
\addpaper
	{A boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{}
	{SIGBOVIK_2017_paper_63}
	{0cm}
	{}

\addtrack{Dog track}{Nonstandard ML}
\addpaper
	{Batch normalization for improved DNN performance, my ass}
	{Joshua A.\ Wise}
	{}
	{SIGBOVIK_2017_paper_32}
	{1cm}
	{}
\addpaper
	{Colonel density estimation}
	{Harish Krishna \textit{et al.}}
	{}
	{SIGBOVIK_2017_paper_67}
	{1cm}
	{}
\addpaper
	{Degenerative adversarial networks}
	{Raphael Gontijo Lopes and Diptodip Deb}
	{}
	{SIGBOVIK_2017_paper_74}
	{1cm}
	{}
\addpaper
	{Stopping GAN violence: Generative unadversarial networks}
	{Samuel Albanie, S\'ebastien Ehrhardt, and Jo\~ao Henriques}
	{}
	{SIGBOVIK_2017_paper_13}
	{1cm}
	{}

@@

\addtrack{Groundhog track}{Putting the ``Under'' in ``Image Understanding''}
\addpaper
	{DeepDoggo: Learning the answer to ``Who's a good dog?''}
	{Benjamin J.\ Lengerich}
	{}
	{SIGBOVIK_2017_paper_69}
	{1cm}
	{}
\addpaper
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad and\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{}
	{SIGBOVIK_2017_paper_22}
	{3cm}
	{}
\addpaper
	{Distinguishing humans from other forms of cattle}
	{Boppity Bob Martinez and Flokkka\textdegree\ Haurilet}
	{}
	{SIGBOVIK_2017_paper_23}
	{3cm}
	{}
\addreview{SIGBOVIK_2017_review-23}{0cm}

\addtrack{Chipmunk track}{New and ``Improved'' Languages}
\addpaper
	{On the Turing completeness of MS PowerPoint}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2017_paper_58}
	{0cm}
	{}
\addpaper
	{Effective multi-threading in Befunge}
	{Zachary Wade}
	{}
	{SIGBOVIK_2017_paper_37}
	{3cm}
	{}
\addpaper
	{Automatic distributed execution of LLVM code using SQL JIT compilation}
	{Mark Raasveldt, Tim Gubner, and Abe Wits}
	{}
	{SIGBOVIK_2017_paper_90}
	{1cm}
	{}
\addpaper
	{WysiScript: Programming via direct syntax highlighting}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2017_paper_71}
	{0cm}
	{}
\addpaper
	{ZM\~{}\~{} \# PRinty\# C with ABC!}
	{Dr.\ Tom Murphy VII, Ph.D.}
	{}
	{SIGBOVIK_2017_paper_73}
	{0cm}
	{}

\addtrack{Insect track}{Debugging}
\addpaper
	{Amazon Web Services: Field observations related to arachnid cohabitation}
	{Riva Riley}
	{}
	{SIGBOVIK_2017_paper_60}
	{0cm}
	{}
\addpaper
	{Blackberry Debugging}
	{Allison M.\ Gardner and Kristen S.\ Gardner}
	{}
	{SIGBOVIK_2017_paper_40}
	{0cm}
	{}

\addtrack{Moose track}{Impure Math and \textbackslash Big Data}
\addpaper
	{Fake news logic}
	{Will Nalls}
	{}
	{SIGBOVIK_2017_paper_91}
	{1.85cm}
	{}
\addreview{SIGBOVIK_2017_review-91}{0cm}
\addpaper
	{RRR for UUU: Exact analysis of pee queue systems with perfect urinal etiquette}
	{Kristen Gardner and Ziv Scully}
	{}
	{SIGBOVIK_2017_paper_75}
	{0cm}
	{}
\addreview{SIGBOVIK_2017_review-75}{0cm}
\addpaper
	{The next 700 type systems}
	{Carlo Angiuli}
	{}
	{SIGBOVIK_2017_paper_33}
	{3cm}
	{}
\addpaper
	{A modular approach to state-of-the-art big data visualization}
	{Keith A.\ Maki}
	{}
	{SIGBOVIK_2017_paper_78}
	{0cm}
	{}
\addpaper
	{Efficient computation of an optimal portmantout}
	{David Renshaw}
	{}
	{SIGBOVIK_2017_paper_34}
	{0cm}
	{}

\addtrack{Raccoon track}{Talkin' Trash}
\addpaper
	{Garbage collection for heaps only a mother could love}
	{Your Parents}
	{}
	{SIGBOVIK_2017_paper_12}
	{1cm}
	{}
\addpaper
	{A new paradigm for robotic dust collection: Theorems, user studies, and a field study}
	{Rachel Holladay and Siddhartha S.\ Srinivasa}
	{}
	{SIGBOVIK_2017_paper_17}
	{0cm}
	{}

\addtrack{Cat track}{Work-\texorpdfstring{\sout{stealing}}\ saving}
\addpaper
	{The Zero-color Theorem: An optimal poster design algorithm}
	{Michael Coblenz}
	{}
	{SIGBOVIK_2017_paper_11}
	{0cm}
	{}
\addreview{SIGBOVIK_2017_review-11}{0cm}
\addpaper
	{Cerebral genus: Dead duck or phoenix?}
	{Oscar I.\ Hernandez}
	{}
	{SIGBOVIK_2017_paper_70}
	{0cm}
	{}

>>>>

\addproceedings{Portrait of Markov}

\addtrack
	[\scalebox{0.1}{\includegraphics{tracks/bear}}\scalebox{0.1}{\includegraphics{tracks/bear}}\scalebox{0.1}{\includegraphics{tracks/bear}}\scalebox{0.1}{\includegraphics{tracks/bear}}]
	{One Track to Rule Them All}{One Track to Find Them}

\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Dicong Qiu}
	{}
	{SIGBOVIK_2018_paper_1}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{mallocd:\ designing a garbage-free nosql data store}
	{igor}
	{}
	{SIGBOVIK_2018_paper_4}
	{0cm}
	{}
\addpaper
	{Ritwik density estimation and analysis using real techniques}
	{Ritwik Gupta, Ritwik Das, and Ritwik Rajendra}
	{}
	{SIGBOVIK_2018_paper_5}
	{0cm}
	{}
\addpaper
	{Towards a formalization of Claude Shannon's masters thesis}
	{andrewtron3000}
	{}
	{SIGBOVIK_2018_paper_7}
	{0cm}
	{}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{Heuristic Ordered-Word Longform Obfuscation, Normally Generated, Creating Abstract
	Nominalizations In Monogrammatic Arrangement Keeping Expected Maximum Yield:\ Study Infers
	Greater Breadth Over Vocabularic Initialization Key Property Regarding Extended
	Sesquipedalian Entries; Notably The Abecedarian Tactics Include Overelaboration, Neologisms,
	Textual Interpretations Twisting Lexical Entries By Eliciting Full Online Resources
	Explaining Possible Exchanges; Often Potential Logorrheic Excesses Require Eventual
	Alternate Listing (Instantiating Zeugma); Energetically Iterating Text Strains Jocularity
	Under Starting Thesis Allocating Humor Until Grand Exit After Conclusion Reaches Obvious
	Nadir Yattering Meaninglessly}
	{Luke Breitfeller}
	{}
	{SIGBOVIK_2018_paper_9}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\addpaper
	{CommieCoin:\ Seizing the means of crypto-production}
	{Marx van Raasveldt \textit{et al.}}
	{}
	{SIGBOVIK_2018_paper_11}
	{0cm}
	{}
\addpaper
	{WordTeX:\ A WYSIPCTWOTCG typesetting tool}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2018_paper_12}
	{0cm}
	{}
\addpaper
	{Transactional memory concurrency verification with Landslide}
	{Ben Blum}
	{}
	{SIGBOVIK_2018_paper_13}
	{0cm}
	{}

@@

\addpaper
	{Automating art snobbiness:\ Dead duck or phoenix?}
	{Dion Ysus and Oscar I.\ Hernandez}
	{}
	{SIGBOVIK_2018_paper_14}
	{0cm}
	{}
\addpaper
	{GradCoin:\ A poor-to-poor electronic cash transfer system}
	{Siddhant Jain}
	{}
	{SIGBOVIK_2018_paper_15}
	{0cm}
	{}
\addpaper
	{Alternary operators:\ Alternative ternary operators}
	{Jim McCann; Your Name Here; and Your Name Here, Evan}
	{}
	{SIGBOVIK_2018_paper_16}
	{0cm}
	{}
\addpaper
	{A definitely not cherry-picked rhetorical analysis of programming languages reviews}
	{Hannah G.\ Ringler and Stefan Muller}
	{}
	{SIGBOVIK_2018_paper_17}
	{0cm}
	{}
\addpaper
	{The fluint8 software integer library}
	{Jim McCann and Tom Murphy VII}
	{}
	{SIGBOVIK_2018_paper_18}
	{0cm}
	{}
\addpaper
	{bashcc:\ Multi-prompt one-shot delimited continuations for Bash}
	{Spencer Baugh and Dougal Pugson}
	{}
	{SIGBOVIK_2018_paper_19}
	{0cm}
	{}
\addpaper
	{COBOLd:\ Gobblin' up COBOL bugs for fun and profit}
	{squaresLab and Mr.\ squaresLab SpouseMan}
	{}
	{SIGBOVIK_2018_paper_20}
	{0cm}
	{}
\addpaper
	{Toward a historically faithful performance of the piano works of Anton\'in Qwe\v{r}t\'y}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2018_paper_21}
	{0cm}
	{}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{}
	{SIGBOVIK_2018_paper_22}
	{0cm}
	{}
\addpaper
	{This grad student studied parapsychology---and you won't believe what he found}
	{David Edelstein}
	{}
	{SIGBOVIK_2018_paper_23}
	{0cm}
	{}
\addpaper
	{Academic Advancement Advice:\ Author Articles as A.\ A.}
	{A.\ A.}
	{}
	{SIGBOVIK_2018_paper_24}
	{0cm}
	{}
